Essays in Computational Management Science

### 2018-05-11 Chapters/sdm-applications.tex

Reinforcement learning has increasing prominence in the media after AlphaZero has won all games from both the best chess grandmasters in the world and the best chess engines. What is incredible about these victories is that AlphaZero has almost no knowledge about chess game and has learned all its movement playing against itself for 4 hours. Basically, it knows only the valid movements and had to learn everything from scratch, which it did using a reinforcement learning algorithm \citep{silver2017mastering, silver2017masteringchess}.

>>>>

Reinforcement learning has increasing prominence in the media after AlphaZero has won all games from both the best chess grandmasters in the world and the best chess engines. What is incredible about these victories is that AlphaZero has almost no knowledge about chess game and has learned all its movement playing against itself for 4 hours. Basically, it knows only the valid movements and had to learn everything from scratch, which it did using a reinforcement learning algorithm\footnote{See also the recent work on modern machine learning and reinforcement learning \citep{aguiar_sdm-go:_2013, wu_kanerva_2018}} \citep{silver2017mastering, silver2017masteringchess}.
